First and foremost, I would like to express my wholehearted gratitude to my advisor, 
Professor Shan Lu, for her generous support and guidance during my PhD. 

The first email I sent to Shan is to ask whether I could provide her name as my potential advisor, when I applied my student visa. 
Shan kindly approved this. 
I am so lucky to begin my independent study with her immediately after I came to US. 
I can still remember the joy in my heart when she told me that she would pick me as her student, after we submit AFix. 

Throughout my PhD, Shan gave me numerous invaluable academic advice, 
ranging from the details of how to present data in my paper to the broad vision of 
how to explore an initial research idea. 
Besides research, 
Shan also teaches me how to better communicate with other people, 
how to manage my time, and how to be confident. 
Shan served as my role model in the past five years. 
I am so fortunate to observe and learn how she learns new knowledge, 
conducts research and succeeds in her career. 
PhD journey is tough. 
I feel extremely thankful for Shan's patience, support and actionable suggestions in each stage. 
I do not think I can get to the destination without her encouragement. 
 
I gratefully thank Professor Ben Liblit and Professor Darko Marinov for their kindly help during and after collaborating. 
Ben and Darko are always encouraging and helpful whenever I encounter research problems. 
Ben also helps me go through all paperwork and payment after Shan left to UChicago. 
I worked in Illinois for around one week, and it is an exciting experience to learn technical skills closely from Darko. 

I would like to thank all other committee members, Professor Remzi Arpaci-Dusseau, 
Professor Aws Albarghouthi, and Professor Xinyu Zhang, for their priceless comments and constructive criticisms on my thesis. 
It is really my honor to have all these professors on my committee. 
I would also thank Professor Loris D'Antoni for coming to my defense and leaving invaluable feedback. 

Thanks also go to every student in Shan's group and fellow students I worked with for 
the opportunity to learn together. 
I worked with Guoliang Jin on my first two research projects, and I want to thank him for helping me through my junior years. 
I want to thank Adrian Nistor for treating me so many lunches and solving so many weird problems I encountered in Illinois.
I want to thank Wei Zhang, Po-Chun Chang, Xiaoming Shi, Dongdong Deng, Rui Gu, Joy Arulraj, 
Joel Sherpelz, Haopeng Liu, and Yuxi Chen for making our group fun and exciting. 

I also want to thank many other people in UWisconsin. 
Thanks to Professor David Page, Professor Michael Swift, Professor Susan Horwitz, 
Professor Jerry Zhu, and Professor Eric Bach for knowledge I learned from their courses. 
Thanks to Angela Thorp for helping me through various administration stuff. 
Thanks to Peter Ohmann for suggestions about how to polish my talk. 
Thanks to my great roommates, Hao Wang, Ce Zhang, Jia Xu, and Huan Wang for giving me such great accompany. 
Thanks to all other good friends, Lanyue Lu, Wenfei Wu, Suli Yang, Yupu Zhang, Yiying Zhang, 
Jie Liu, Wentao Wu, Wenbin Fang, Weiyan Wang, Xiaozhu Meng, Junming Xu, Yimin Tan, Yizheng Chen, Ji Liu, Jun He, and Ao Ma for their help and support in different ways. 

I benefit a lot from my summer intern in NEC Labs America. 
I want to thank the company as well as my mentor Dr. Min Feng, for providing a terrific internship experience. 
 
Last but not least, I want to thank my parents back in China for their unconditional love and trust. 
Whenever I struggle with my PhD life, my parents are always supportive and encouraging. 
My work would not be nearly as meaningful without them. 
No words can express my gratitude and love to them. 
I dedicate the whole thesis to the most important persons in my life.  
