\svnidlong{$LastChangedBy$}{$LastChangedRevision$}{$LastChangedDate$}{$HeadURL: http://freevariable.com/dissertation/branches/diss-template/frontmatter/frontmatter.tex $}
\vcinfo{}

%%% SOME OF THIS CODE IS ADAPTED FROM THE VENERABLE withesis.cls

% COPYRIGHT PAGE
%  - To include a copyright page use \copyrightpage
\copyrightpage

% DEDICATION
\begin{dedication}
	\emph{To my parents, Zuoyu Song and Cuihua Fu.}
\end{dedication}

%% BEGIN PAGESTYLE

%%% You can pick a pagestyle if you want; see the memoir class
%%% documentation for more info.  The default ``deposit'' option meets
%%% the UW thesis typesetting requirements but is probably
%%% unsatisfactory for making a version of your dissertation that
%%% won't be deposited to the graduate school (e.g. for web or a nice
%%% printed copy)

\chapterstyle{deposit}
\pagestyle{deposit}


% ACKNOWLEDGMENTS
\begin{acks}
\input{frontmatter/acks}
\end{acks}

% CONTENTS, TABLES, FIGURES
\renewcommand{\printtoctitle}[1]{\chapter*{#1}}
\renewcommand{\printloftitle}[1]{\chapter*{#1}}
\renewcommand{\printlottitle}[1]{\chapter*{#1}}

\renewcommand{\tocmark}{}
\renewcommand{\lofmark}{}
\renewcommand{\lotmark}{}

\renewcommand{\tocheadstart}{}
\renewcommand{\lofheadstart}{}
\renewcommand{\lotheadstart}{}

\renewcommand{\aftertoctitle}{}
\renewcommand{\afterloftitle}{}
\renewcommand{\afterlottitle}{}

\renewcommand{\cftchapterfont}{\normalfont} 
\renewcommand{\cftsectionfont}{\itshape} 
\renewcommand{\cftchapterpagefont}{\normalfont} 
\renewcommand{\cftchapterpresnum}{\bfseries} 
\renewcommand{\cftchapterleader}{\hskip2mm} 
\renewcommand{\cftsectionleader}{\hskip2mm} 
\renewcommand{\cftchapterafterpnum}{\cftparfillskip} 
\renewcommand{\cftsectionafterpnum}{\cftparfillskip} 

% \captionnamefont{\small\sffamily} 
% \captiontitlefont{\small\sffamily} 

% \renewcommand{\contentsname}{contents}
% \renewcommand{\listfigurename}{list of figures}
% \renewcommand{\listtablename}{list of tables}

\tableofcontents

\clearpage
\listoftables

\clearpage
\listoffigures

%\clearpage
% NOMENCLATURE
 %\begin{conventions}
 %\begin{description}
 % \item{\makebox[0.75in][l]{term}
 %        \parbox[t]{5in}{definition\\}}
 % \end{description}
 %\input{frontmatter/conventions}
 %\end{conventions}

%\advisorname{Gottlob Frege}
%\advisortitle{Professor}
% ABSTRACT
%\begin{umiabstract}
%  \input{frontmatter/abstract}
%\end{umiabstract}

\begin{nomenclature}
%\begin{description}

\begin{enumerate}

\item{{\textit{Performance bug:}}}
performance bugs are software implementation mistakes 
that can cause inefficient execution. 
We will use performance bugs
and performance problems interchangeably in this thesis 
following previous work in this 
area~\citep{Alabama,perf.fse10}.


\item{{\textit{Functional bug:}}}
functional bugs are software defects that lead to functional misbehavior, 
such as incorrect outputs, crashes, and hangs. 
Functional bugs include semantic bugs, 
memory bugs and concurrency bugs~\citep{LiASID06}.



\item{{\textit{Efficiency rule:}}}
efficiency rules are principles inside programs, 
violations of which will lead to inefficient execution. 
Efficiency rules usually contain two components, 
which indicate where and how a particular code transformation 
can be conducted to improve performance, 
while preserving original functionality. 


\item{{\textit{Root-cause information:}}}
for a particular failure, root-cause information includes a static code region causing the failure, 
explanation why the failure happens, and potential fix suggestions.


\item{{\textit{Inefficient loop:}}}
inefficient loops are loops that conduct inefficient computation due to performance bugs.

\item{{\textit{Diagnosis latency:}}}
diagnosis latency is the time it takes to figure out the root cause of a failure.                    
It is measured by
how many failure runs are needed in order to conduct failure diagnosis. 


\item{{\textit{Runtime overhead:}}}
runtime overhead is measured by comparing normal execution with monitored execution. 


%\item{\makebox[0.75in][l]{$V$}}    Voltage

%\item{\makebox[0.75in][l]{\$}}     US Dollars

\end{enumerate}
%\end{description}
\end{nomenclature}

%\clearpage
\begin{abstract}
  \input{frontmatter/abstract}
\end{abstract}

\clearpage\pagenumbering{arabic}

%%% END STUFF TAKEN FROM WITHESIS EXAMPLE FILE
