




\section{Root Causes of Performance Bugs}
\label{sec:3_root}

There are a large variety of potential root causes for inefficient code, 
such as poorly designed algorithms, non-optimal data structures, cache-unfriendly data layouts, etc. 
Our goal here is not to discover previously unheard-of root causes, 
but to check whether there are common root-cause patterns among 
real-world performance bugs that bug detection and diagnosis work can focus on.

\begin{table*}[tb!]
\begin{adjustwidth}{-1in}{-1in}
\scriptsize
\centering
{

\begin{tabular}{lcccccc}
\toprule
\multicolumn{1}{c}{\bf Root Causes for Performance Bugs} &Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\midrule
\multicolumn{1}{l}{{\bf Wrong Branch:} branch selection leading to performance loss}
&2&0&2&7&6&17\\
\midrule
\multicolumn{1}{l}{{\bf Resultless:} not generating desired results}
&3&5&4&20&10&42\\
\midrule
\multicolumn{1}{l}{{\bf Redundancy:} generating the same results repeatedly}
&13&3&4&6&5&31\\
\midrule
\multicolumn{1}{l}{{\bf Synchronization Issues:} inefficient synchronization among threads}
&6&1&0&1&8&16\\
\midrule
\multicolumn{1}{l}{{\bf Others:} all the bugs not belonging to the above four categories}
&5&1&1&3&3&13\\
\bottomrule

\end{tabular}
}
\end{adjustwidth}
\caption{Root cause categorization in Section~\ref{sec:3_root}}
\label{tab:3_root}
\end{table*}

Our study shows that the majority of real-world performance bugs in our study 
are covered by only a couple of root-cause categories (Table~\ref{tab:3_root}).

\underline{\it Wrong Branch} 
A non-negligible portion of performance bugs are branch-related.
There are three situations for bugs under this category. 
Firstly, wrong branches lead to some slow code paths. 
For example, when Mozilla\#231300 is triggered, 
Firefox would use separate system calls to move files 
in the same directory one by one instead of using one single system call to move them altogether. 
Seconly, wrong branches lead to unnecessary computation or execution. 
For example, when Mozilla\#258793 is triggered, 
Firefox will call draw functions for background figures, which actually do not exist. 
Finally, wrong branches lead to inefficient functionalities,
such as the {\it No Cache} example shown in Figure~\ref{fig:MySQL26527}. 

\underline{\it Resultless} 
Around one third of performance bugs are caused by resultless codes. 
Buggy codes rarely generate results when these bugs are triggered.
Bugs in this category can be further categorized along two dimensions: 
according to different granularities, 
resultless bugs can be divided into loop-related bugs and not loop-related bugs; 
based on whether semantic information is needed to identify resultless, 
resultless bugs can be divided into semantic resultless, and non-semantic resultless.
When {\it Intensive GC} shown in Figure~\ref{fig:Mozilla515287} triggered, 
the loop conducting garbage collection scans all heap objects, 
but rarely finds free objects with reference number 0 and deallocate them. 
This bug is loop-related and non-semantic.  
{\it Transparent Draw} in Figure~\ref{fig:Mozilla66461} is not loop-related, 
and semantic information is needed to know that drawing a transparent figure does not generate any results.

\underline{\it Redundancy} 
Redundancy means generating the same results repeatedly. 
Intuitively, we can remove repeated work and improve performance. 
According to different code granularity to observe redundant work, 
bugs in this category can be divided into redundant snippets, 
cross-iteration redundancy, and cross-loop redundancy.  
For example, in Chrome\#70153, 
both software and GPU will render the same video redundantly, 
and this bug is categorized as redundant snippets. 
In the {\it Bookmark All} example shown in Figure~\ref{fig:Mozilla515287}, 
Firefox will start, commit, and destroy a transaction for each tab in each iteration, 
and there is a lot of redundant work across different iterations. 
There are also bugs caused by cross-loop redundancy, like Mozilla\#35294

\underline{\it Synchronization Issues}
Unnecessary synchronization that intensifies thread competition 
is also a common root cause, as shown in the {\it Slow Fast-Lock} 
bug (Figure~\ref{fig:MySQL26527}). 
These bugs are especially common in server applications, 
contributing to 6 out of 16 Apache server bugs and 7 out of 25 MySQL server bugs.

\underline{\it Others}
There are also bugs that do not fall into above categories. 
For these bugs, developers find more efficient methods to optimize original codes.
For example, in order to accelerate the slow startup of GPU process reported in Chrome\#59711, 
developers use one extra thread to collect expensive GPU information. 
For MySQL\#14637, MySQL developers replace byte-wise parsing by using four-byte-wise parsing 
to accelerate trimming blank characters from the end of a string. 
