\section{How Performance Bugs Are Fixed}
\label{sec:3_fix}

\begin{table*}[tb!]
\begin{adjustwidth}{-1in}{-1in}
\scriptsize
\centering
{
\begin{tabular}{lcccccc}
\toprule
\multicolumn{1}{c}{\bf How to Fix Performance Bugs} &Apache&Chrome&GCC&Mozilla&MySQL&Total\\
\midrule
\multicolumn{1}{l}{{\bf Change Condition:} {a condition is added or modified} }
&3&3&5&13&9&36\\
\midrule
\multicolumn{1}{l}{{\bf In-place Call Change:} {replace call sequences in the exact same place} }
&5&1&0&12&10&28\\
\midrule
\multicolumn{1}{l}{{\bf Memoization:} {reuse results from previous computation}}
&9&1&3&2&3&18\\
\midrule
 \multicolumn{1}{l}{{\bf Batch:} {batch computation to eliminate redundancy}}
&4&3&1&6&1&15\\
\midrule
\multicolumn{1}{l}{{\bf Others:} all the bugs not belonging to the above four categories}
&4&2&2&3&5&16\\
\bottomrule
\end{tabular}
}
\end{adjustwidth}
\caption{How to fix performance bugs in Section~\ref{sec:3_fix}.}
\label{tab:3_fix}
\end{table*}

There are four common strategies in fixing performance bugs, as shown in Table~\ref{tab:3_fix}.

\underline{\it Change Condition} The most common fix strategy is {\it Change Condition}. 
It is used in 36 patches, in which code units not always generating 
results are conditionally skipped, 
a fast path is changed to be executed, or the same functionality is realized in a more efficient way. 
For example, Draw is conditionally skipped to fix {\it Transparent Draw} (Figure~\ref{fig:Mozilla66461}), 
and cache will be used to fix {\it No Cache} (Figure~\ref{fig:MySQL26527} ).

\underline{\it In-place Call Change} 
The second most common strategy is {\it In-place Call Change}. 
By using this strategy, 
developers replace or reorganize the call sequence in the exact same place. 
The performance gain can be achieved whenever changed codes are executed. 
For example, in order to fix Mozilla\#103330, 
developers replace the \Code{setLength} and \Code{Append} call combination with \Code{Assign}.

\underline{\it Memoization} fixes 18 bugs by reusing results 
from previous computation. 
For example, in order to fix Mozilla\#409961, 
developers move \Code{do\_QueryInterface} outside the buggy loop, instead of calling it in each iteration.  

\underline{\it Batch} strategy is used in 15 patches. 
For example, {\it Bookmark All} in Figure~\ref{fig:Mozilla490742} is fixed by this strategy.   

\underline{\it Are patches complicated?}
Most performance bugs in our study can be fixed through simple changes. 
In fact, 41 out of 110 bug patches contain five or fewer lines of code changes. 
The median patch size for all examined bugs is 9 lines of code.
The small patch size is a result of the above fixing strategies.
Many change condition patches are small. 
Most in-place call change, memoization, and batch patches do not require implementing new function calls.

